Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-05-15 ms.tex
added acknowledgments file, put some basic stuff in there.
minor tweak: author list idea.

\title{Enzo: An Adaptive Mesh Refinement Code for Astrophysics}
\author{Authors}

@@

We now describe each of the numerical methods in detail.  The structure of this section mirrors the previous one, in which each method was briefly described; here we present the details.

\input{numerical-amr}
\input{numerical-ppm}
\input{numerical-muscl} % new
%\input{numerical-mhd-dedner} % new (combined with muscl)
\input{numerical-mhd-ct}  % new
\input{numerical-zeus}
\input{numerical-gravity}
\input{numerical-particle}
\input{numerical-chemistry}
\input{numerical-cooling} % new
\input{numerical-radiation-homogeneous} % new
\input{numerical-radiation-raytracing} % new
\input{numerical-radiation-fld} % new
\input{numerical-conduction} % new
\input{numerical-starformation}
\input{numerical-timestep}
\input{numerical-analysis} % new

@@

>>>>

\title{Enzo: An Adaptive Mesh Refinement Code for Astrophysics}
\author{The Enzo Collaboration:}
\author{author 1}
\author{author 2}
\author{author 3...}

@@

We now describe each of the numerical methods in detail.  The
structure of this section mirrors that of Section~\ref{sec.overview},
in which each method was briefly described.

\input{numerical-amr}
\input{numerical-ppm}
\input{numerical-muscl} % new
\input{numerical-mhd-dedner} % new (combined with muscl)
\input{numerical-mhd-ct}  % new
\input{numerical-zeus}
\input{numerical-gravity}
\input{numerical-particle}
\input{numerical-chemistry}
\input{numerical-cooling} % new
\input{numerical-radiation-homogeneous} % new
\input{numerical-radiation-raytracing} % new
\input{numerical-radiation-fld} % new
\input{numerical-conduction} % new
\input{numerical-starformation}
\input{numerical-timestep}
\input{numerical-analysis} % new

@@

\input{acknowledgments}

### 2013-05-15 numerical-analysis.tex

At user-specified intervals, the tracer particles output their data
in a streaming format into a binary file.  The data written out
typically includes the tracer particle's unique ID, position, velocity, density,
and temperature, but is easily extensible to output any grid-based
quantity that a user requires.  This capability has been used quite
effectively in several papers, including \citet{2010ApJ...715.1575S}
and \citet{2012ApJ...748...12S}.

>>>>

At user-specified intervals, the tracer particles output their data
in a streaming format into a binary file.  The data written out
typically includes the tracer particle's unique ID, position, velocity, density,
and temperature, but is easily extensible to output any grid-based
quantity that a user requires.  This capability has been used quite
effectively in several papers, including \citet{2010ApJ...715.1575S}
and \citet{2012ApJ...748...12S}. It is crucial to keep in mind that
tracer particles model some Lagrangian fluid trajectories. The fluid
on the grid, however, models the motion of all the mass and represents
the average quantity in a grid cells volume. Consequently, after some
evolution tracer particles, which even if they initially had the same
density distribution as the gas, will not have the same density
distribution as the fluid. They tend to accumulate at stagnation points
of the flow, e.g., and care has to be taken in using these particles
appropriately. They can be very useful, e.g. to study a variety of
histories of the hydrodynamic quantities in Lagrangian fluid elements
and evaluate complex chemical and cooling models in regard to the
simpler ones used in the actual numerical evolution.
